---
title: "HEIC image converter"
author: "Matthew Cox"
date: "2025-02-25"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction

The purpose of this script is to convert pictures taken by an iphone (.heic) into .jpeg files for analysis.

```{r}
library(magick)
```


# INPUT/OUTPUT FOLDERS HERE

Replace the text in the "quotes" with your input file directory filled with HEIC images, and the folder you'd like the final converted images to be saved to.

Once your file paths are added, simply run the whole script and your images will be converted!

```{r}
# Set input and output directories
input_dir <- "~/Desktop/MDIBL/Haller Lab/fish pictures/HEIC"
output_dir <- "~/Desktop/MDIBL/Haller Lab/fish pictures/JPEG/"
```


```{r}
# Create output directory if it doesn't exist
if (!dir.exists(output_dir)) {
  dir.create(output_dir)
}

# List all HEIC files
input_list <- list.files(input_dir, pattern = "\\.HEIC$", full.names = TRUE)

# Loop through each image file
for (image_path in input_list) {
  # Get the image name without the extension
  image_name <- tools::file_path_sans_ext(basename(image_path))
  
  # Read image with full path
  image <- image_read(image_path)
  
  # Save as JPEG in the output directory
  output_path <- file.path(output_dir, paste0(image_name, ".jpeg"))
  image_write(image, path = output_path, format = "jpeg")
  
  cat("Converted:", image_path, "->", output_path, "\n")
}


```

